---
title: "Final Report"
author: "Justin Chan and Isaac Plotkin"
date: "3/12/2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis: Final Project
## Research Question and Modeling Objective
The research question we have is how to best predict car prices using the various car features from our dataset. Therefore, our modeling objective is to create the best possible linear model using the most optimal set of features in our car dataset. Then we will be able to use this model to make predictions on car prices for new cars. We used \href{https://www.ijrte.org/wp-content/uploads/papers/v8i5s/E10100285S20.pdf}{\emph{Predicting True Value of Used Car using Multiple Linear Regression Model}} (D’Costa et al) and \href{https://www.temjournal.com/content/81/TEMJournalFebruary2019_113_118.pdf}{\emph{Car Prediction using Machine Learning Techniques}} (Gegic et al) as references for this paper.

## Description of Data and Response Variable
### Data
The observations (rows) in the dataset are cars with the columns being various features of the car. The dataset includes 205 rows and 26 columns. The first column is an observation index and the last column is \textbf{carprice} which is the response variable we are trying to predict. The rest of the columns are the 24 car features. There are 205 cars that we can use for our linear regression model.

The data was originally collected from various market surveys of different types of cars across the United States market around 1987 to learn how to price cars in China depending on the American market. There is an assumption that the cars in the dataset have been randomly chosen from the set of cars in the various market surveys. 

The car dataset is from Kaggle: <https://www.temjournal.com/content/81/TEMJournalFebruary2019_113_118.pdf>

```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(broom)
library(cowplot)
library(patchwork)
library(MuMIn)
library(rms)
```
```{r car data download, echo=FALSE, message=FALSE, warning=FALSE}
car_data <- read_csv("data/CarPrice_Assignment.csv")
```


### General Description of Variables

The following is the data dictionary of our dataset that gives a clear, general description of our variables/covariates that can be used in the model.

\textbf{symboling}: Its assigned insurance risk rating (Categorical)

\textbf{carCompany}: Name of car campany (Categorical)

\textbf{fueltype}: Car fuel type i.e gas or diesel (Categorical)

\textbf{aspiration}: Aspiration used in a car (Categorical)

\textbf{doornumber}: Number of doors in a car (Categorical)

\textbf{carbody}: Body of car (Categorical)

\textbf{drivewheel}: Type of drive wheel(Categorical)

\textbf{enginelocation}: Location of car engine (Categorical)

\textbf{wheelbase}: Wheelbase of car (Numeric)

\textbf{carlength}: Length of car (Numeric)

\textbf{carwidth}: Width of car (Numeric)

\textbf{carheight}: Height of car (Numeric)

\textbf{curbweight}: The weight of a car withoput occupants or baggage (Numeric)

\textbf{enginetype}: Type of engine (Categorical)

\textbf{cylindernumber}: Cylinder placed in car (Categorical)

\textbf{enginesize}: Size of car (Numeric)

\textbf{fuelsystem}: Fuel Sytem of car (Categorical)

\textbf{boreratio}: Boreration of car (Numeric)

\textbf{stroke}: Stroke or volume inside the engine (Numeric)

\textbf{compressionratio}: compression ratio of car (Numeric)

\textbf{horsepower}: Horsepower (Numeric)

\textbf{peakrpm}: car peak rpm (Numeric)

\textbf{citympg}: mileage in city (Numeric)

\textbf{highwaympg}: mileage on highway (Numeric)

\textbf{price}: price of car (Numeric)



### Response Variable: Price
The response variable, \textbf{price}, is the price of the car in our dataset. In order to be able to predict \textbf{price}, we performed some initial univariate analysis of \textbf{price} to observe its spread in the dataset.

```{r price, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = car_data, aes(x = price)) + 
  geom_histogram() + 
  labs(x = "Price", 
       y = "Counts", 
       title = "Price Distribution")

```

\textbf{Price} seems unimodal meaning that there is one peak. It also seems to be skewed to the right where there are many datapoints that have \textbf{price} around 5,000-10,000 but there are a few outliers that have \textbf{price} greater than \$25,000. To follow up with our analysis, we also created summary statistics for \textbf{price} to see if the statistics reflected the graph we observed.

```{r price summary statistics, echo=FALSE, message=FALSE, warning=FALSE}
car_data %>%
  summarise(min = min(price), 
            q1 = quantile(price, probs = c(0.25)), 
            median = median(price), 
            q3 = quantile(price, probs = c(0.75)), 
            max = max(price), 
            iqr = IQR(price), 
            mean = mean(price), 
            std_dev = sd(price)
            )

```

Our summary statistics further support the plot of \textbf{price} distribution. Since the mean (\$13,276) is much larger than the median (\$10,295) and $q1 - min$ (\$2,670) is much less than $max - q3$ (\$28,897), this proves that the distribution is right skewed and that there are outliers with high \textbf{price}.

## EDA
### Univariate
In the following code block, we plotted the 23 covariates/possible predictor variables to do a simple univariate analysis. We used bar graphs for categorical variables and histograms for continuous variables. We formatted the graphs to be able to optimize for space on the pdf and still be able to see the visualization analysis for each variable.
```{r univariate predictor variables, echo=FALSE, message=FALSE, warning=FALSE}
p1 <- ggplot(data = car_data, aes(x = symboling)) + 
  geom_bar() + 
  labs(x = "Symboling", 
       y = "Counts", 
       title = "Symboling Distribution")

p2 <- ggplot(data = car_data, aes(x = drivewheel)) + 
  geom_bar() + 
  labs(x = "Drive Wheel", 
       y = "Counts", 
       title = "Drive Wheel Distribution")

p3 <- ggplot(data = car_data, aes(x = fueltype)) + 
  geom_bar() + 
  labs(x = "Fuel Type", 
       y = "Counts", 
       title = "Fuel Type Distribution")

p4 <- ggplot(data = car_data, aes(x = aspiration)) + 
  geom_bar() + 
  labs(x = "Aspiration", 
       y = "Counts", 
       title = "Aspiration Distribution")

p5 <- ggplot(data = car_data, aes(x = doornumber)) + 
  geom_bar() + 
  labs(x = "Door Number", 
       y = "Counts", 
       title = "Door Number Distribution")

p6 <- ggplot(data = car_data, aes(x = carbody)) + 
  geom_bar() + 
  labs(x = "Car Body", 
       y = "Counts", 
       title = "Car Body Distribution")

p7 <- ggplot(data = car_data, aes(x = CarName)) + 
  geom_bar() + 
  labs(x = "Car Name", 
       y = "Counts", 
       title = "Car Name Distribution")

p8 <- ggplot(data = car_data, aes(x = wheelbase)) + 
  geom_histogram() + 
  labs(x = "Wheelbase", 
       y = "Counts", 
       title = "Wheelbase Distribution")

p9 <- ggplot(data = car_data, aes(x = carlength)) + 
  geom_histogram() + 
  labs(x = "Car Length", 
       y = "Counts", 
       title = "Car Length Distribution")

p10 <- ggplot(data = car_data, aes(x = carwidth)) + 
  geom_histogram() + 
  labs(x = "Car Width", 
       y = "Counts", 
       title = "Car Width Distribution")

p11 <- ggplot(data = car_data, aes(x = carheight)) + 
  geom_histogram() + 
  labs(x = "Car Height", 
       y = "Counts", 
       title = "Car Height Distribution")

p12 <- ggplot(data = car_data, aes(x = curbweight)) + 
  geom_histogram() + 
  labs(x = "Curb Weight", 
       y = "Counts", 
       title = "Curb Weight Distribution")

p13 <- ggplot(data = car_data, aes(x = enginetype)) + 
  geom_bar() + 
  labs(x = "Engine Type", 
       y = "Counts", 
       title = "Engine Type Distribution")

p14 <- ggplot(data = car_data, aes(x = cylindernumber)) + 
  geom_bar() + 
  labs(x = "Cylinder Number", 
       y = "Counts", 
       title = "Cylinder Number Distribution")

p15 <- ggplot(data = car_data, aes(x = enginesize)) + 
  geom_histogram() + 
  labs(x = "Engine Size", 
       y = "Counts", 
       title = "Engine Size Distribution")

p16 <- ggplot(data = car_data, aes(x = fuelsystem)) + 
  geom_bar() + 
  labs(x = "Fuel System", 
       y = "Counts", 
       title = "Fuel System Distribution")

p17 <- ggplot(data = car_data, aes(x = boreratio)) + 
  geom_histogram() + 
  labs(x = "Bore Ratio", 
       y = "Counts", 
       title = "Bore Ratio Distribution")

p18 <- ggplot(data = car_data, aes(x = stroke)) + 
  geom_histogram() + 
  labs(x = "Stroke", 
       y = "Counts", 
       title = "Stroke Distribution")

p19 <- ggplot(data = car_data, aes(x = compressionratio)) + 
  geom_histogram() + 
  labs(x = "Compression Ratio", 
       y = "Counts", 
       title = "Compression Ratio Distribution")

p20 <- ggplot(data = car_data, aes(x = horsepower)) + 
  geom_histogram() + 
  labs(x = "Horsepower", 
       y = "Counts", 
       title = "Horsepower Distribution")

p21 <- ggplot(data = car_data, aes(x = peakrpm)) + 
  geom_histogram() + 
  labs(x = "Peak RPM", 
       y = "Counts", 
       title = "Peak RPM Distribution")

p22 <- ggplot(data = car_data, aes(x = citympg)) + 
  geom_histogram() + 
  labs(x = "City MPG", 
       y = "Counts", 
       title = "City MPG Distribution")

p23 <- ggplot(data = car_data, aes(x = highwaympg)) + 
  geom_histogram() + 
  labs(x = "Highway MPG", 
       y = "Counts", 
       title = "Highway MPG Distribution")

(p1+p2+p3)/(p4+p5+p8)
(p9+p10+p11)/(p12+p13+p14)
(p15+p17+p18)/(p19+p20+p21)
(p22+p23)/(p6 + p16)
```

From the first six graphs, most of the bar graphs have uneven distribution of observations across all categories. For the histograms, they all seemed to be unimodal, but some seemed a bit skewed to the right with outliers. Moving onto the next six graphs, the two bar graphs seems very skewed where one category in \textbf{enginetype} and \textbf{cylindernumber} have most of the observations. For the histograms, most of the them seem either unimodal or bimodal and are mostly skewed to the right. The next six graphs are all histograms where most of them have smaller peaks. A third of the histograms seem to have peak in the middle. Another third seem to have a peak on the left and are skewed right. The last third have a peak a bit to the right and are a little skewed to the left. For the next four graphs, the histograms seem to be trimodal where the middle peak is generally the highest and the bar graphs have two categories that have most of the observations. The next last graph has too many categories that have a count of 1 with a few of the categories having a count of 6.

After looking at all the graphs, we wanted to see the summary statistics of the univariate variables so we ran the summary method to see the individual statistics of each of our possible covariates.

```{r predictor variables summary statistics, echo=FALSE, message=FALSE, warning=FALSE}
summary(car_data)
```

From these visualizations and statistics, we found the general distributions of each individual covariate which is always good to know before modeling. As we move onto bivariate analysis, we want to see how these distributions change when including price values to plot against them.

## Bivariate 
For bivariate analysis, we wanted to analyze each covariate vs \textbf{price} to see the relationship between each one. We want to be able to see first if a covariate could be used to distinguish price values for cars and see if there is a linear relationship between the predictor variable and our response variable. The following graphs show us \textbf{price} vs each individual covariate using box plots and scatter plots for categorical and continuous variables.

```{r bivariate predictor variables, echo=FALSE, message=FALSE, warning=FALSE}
b1 <- ggplot(data = car_data, aes(x = as.factor(symboling), y = price)) + 
  geom_boxplot() + 
  labs(x = "Symboling", 
       y = "Price", 
       title = "Price vs Symboling")

b2 <- ggplot(data = car_data, aes(x = drivewheel, y = price)) + 
  geom_boxplot() + 
  labs(x = "Drive Wheel", 
       y = "price", 
       title = "Price vs Drive Wheel")

b3 <- ggplot(data = car_data, aes(x = fueltype, y = price)) + 
  geom_boxplot() + 
  labs(x = "Fuel Type", 
       y = "Price", 
       title = "Price vs Fuel Type")

b4 <- ggplot(data = car_data, aes(x = aspiration, y = price)) + 
  geom_boxplot() + 
  labs(x = "Aspiration", 
       y = "Price", 
       title = "Price vs Aspiration")

b5 <- ggplot(data = car_data, aes(x = doornumber, y = price)) + 
  geom_boxplot() + 
  labs(x = "Door Number", 
       y = "Price", 
       title = "Price vs Door Number")

b6 <- ggplot(data = car_data, aes(x = carbody, y = price)) + 
  geom_boxplot() + 
  labs(x = "Car Body", 
       y = "Price", 
       title = "Price vs Car Body")

b7 <- ggplot(data = car_data, aes(x = CarName, y = price)) + 
  geom_boxplot() + 
  labs(x = "Car Name", 
       y = "Price", 
       title = "Price vs Car Name")

b8 <- ggplot(data = car_data, aes(x = wheelbase, y = price)) + 
  geom_point() + 
  labs(x = "Wheelbase", 
       y = "Price", 
       title = "Price vs Wheelbase")

b9 <- ggplot(data = car_data, aes(x = carlength, y = price)) + 
  geom_point() + 
  labs(x = "Car Length", 
       y = "Price", 
       title = "Price vs Car Length")

b10 <- ggplot(data = car_data, aes(x = carwidth, y = price)) + 
  geom_point() + 
  labs(x = "Car Width", 
       y = "Price", 
       title = "Price vs Car Width")

b11 <- ggplot(data = car_data, aes(x = carheight, y = price)) + 
  geom_point() + 
  labs(x = "Car Height", 
       y = "Price", 
       title = "Price vs Car Height")

b12 <- ggplot(data = car_data, aes(x = curbweight, y = price)) + 
  geom_point() + 
  labs(x = "Curb Weight", 
       y = "Price", 
       title = "Price vs Curb Weight")

b13 <- ggplot(data = car_data, aes(x = enginetype, y = price)) + 
  geom_boxplot() + 
  labs(x = "Engine Type", 
       y = "Price", 
       title = "Price vs Engine Type")

b14 <- ggplot(data = car_data, aes(x = cylindernumber, y = price)) + 
  geom_boxplot() + 
  labs(x = "Cylinder Number", 
       y = "Price", 
       title = "Price vs Cylinder Number")

b15 <- ggplot(data = car_data, aes(x = enginesize, y = price)) + 
  geom_point() + 
  labs(x = "Engine Size", 
       y = "Price", 
       title = "Price vs Engine Size")

b16 <- ggplot(data = car_data, aes(x = fuelsystem, y = price)) + 
  geom_boxplot() + 
  labs(x = "Fuel System", 
       y = "Price", 
       title = "Price vs Fuel System")

b17 <- ggplot(data = car_data, aes(x = boreratio, y = price)) + 
  geom_point() + 
  labs(x = "Bore Ratio", 
       y = "Price", 
       title = "Price vs Bore Ratio")

b18 <- ggplot(data = car_data, aes(x = stroke, y = price)) + 
  geom_point() + 
  labs(x = "Stroke", 
       y = "Price", 
       title = "Price vs Stroke")

b19 <- ggplot(data = car_data, aes(x = compressionratio, y = price)) + 
  geom_point() + 
  labs(x = "Compression Ratio", 
       y = "Price", 
       title = "Price vs Compression Ratio")

b20 <- ggplot(data = car_data, aes(x = horsepower, y = price)) + 
  geom_point() + 
  labs(x = "Horsepower", 
       y = "Price", 
       title = "Price vs Horsepower")

b21 <- ggplot(data = car_data, aes(x = peakrpm, y = price)) + 
  geom_point() + 
  labs(x = "Peak RPM", 
       y = "Price", 
       title = "Price vs Peak RPM")

b22 <- ggplot(data = car_data, aes(x = citympg, y = price)) + 
  geom_point() + 
  labs(x = "City MPG", 
       y = "Price", 
       title = "Price vs City MPG")

b23 <- ggplot(data = car_data, aes(x = highwaympg, y = price)) + 
  geom_point() + 
  labs(x = "Highway MPG", 
       y = "Price", 
       title = "Price vs Highway MPG")

(b1+b2+b3)/(b4+b5+b8) # Wheelbase, symboling, drive wheel, aspiration
(b9+b10+b11)/(b12+b13+b14) # Cylinder num, curb weight, car length, car width
(b15+b17+b18)/(b19+b20+b21) # Engine size, horsepower, bore ration
(b22+b23)/(b6 + b16) # fuel system, city mpg, highway mpg
```

When choosing initial variables to choose for our linear model, we wanted to find scatter plots that had a clear linear relationship and box plots where categories had different median values and price ranges. From our first six graphs, \textbf{symboling} and \textbf{drivewheel} had categories that had different distributions for \textbf{price}, so they are possible covariates. \textbf{Aspiration} and \textbf{wheelbase} seemed pretty reasonable to be covariates so they were also allowed to continue onto the next stage. \textbf{Fueltype} and \textbf{doornumber} were left out due to the minimal difference between their categories in the box plots. Out of the next six graphs analyzed, \textbf{carlength}, \textbf{carwidth}, and \textbf{curbweight} had the most clear linear relationship from the scatter plots. \textbf{Carheight} seemed to have a weak linear relationship and was eliminated. From the box plots, it seemed like the \textbf{cylindernumber} had each of its field to have their unique distributions for \textbf{price} which allowed it to continue as a possible covariate. \textbf{Enginetype} seemed to have much more outliers that caused more overlapping of price ranges across categories so we decided to leave it out of further analysis. For the next six graphs, the scatter plots that looked like they had a linear relationship were \textbf{enginesize}, \textbf{boreratio}, and \textbf{horsepower}. The other three predictor variables, \textbf{compressionratio}, \textbf{stroke}, and \textbf{peakrpm} did not seem to have any linear relationship with \textbf{price} so they were excluded as covariates. Of the next four graphs presented, \textbf{citympg} and \textbf{highwaympg} have a decreasing linear relationship between \textbf{price} so they are allowed to be included for further analysis. \textbf{Fuelsystem} also seemed that it could be possible to be used as a covariate based on a bit of the spread across the categories. On the other hand, \textbf{carbody} categories have quite a bit of overlapping across categories which caused us to eliminate it from further analysis. The last graph, \textbf{carName}, has both make and model of each car so there is only one car in each bin. Therefore, it seems to be useful, but there is not enough cars per category to accurately estimate price. Essentially, there were too many categories to be able to predict price so in order to avoid overfitting, \textbf{carname} was excluded from further analysis.

### Multivariate
Mutlivariate analysis will be used to determine if there was interactions between particular covariates. Specifically the ones we believed that would be used in the model and seemed to be associated with each other. The multivariate analysis we did was against \textbf{highwaympg} and \textbf{citympg} since there were miles per gallon variables and would probably be associated with each other. In addition to these two covariates, it was believed that \textbf{carlength}, \textbf{carwidth}, and \textbf{curbweight} would also have interactions since the bigger the car, generally the bigger the width, length and weight of the car. Below are scatter plots of the covariates plotted against each other. \textbf{Price} is colored with lighter blue representing high car price and dark blue being low car prices.

```{r multivariate predictor variables, echo=FALSE, message=FALSE, warning=FALSE}

m1 <- ggplot(data = car_data, aes(x = highwaympg, y = citympg, color = price)) + 
  geom_point() + 
  labs(x = "Highway MPG", 
       y = "City MPG", 
       title = "City MPG vs Highway MPG")


m2 <- ggplot(data = car_data, aes(x = carlength, y = carwidth, color = price)) + 
  geom_point() + 
  labs(x = "Car Length", 
       y = "Car Width", 
       title = "Car Width vs Car Length")

m3 <- ggplot(data = car_data, aes(x = carlength, y = curbweight, color = price)) + 
  geom_point() + 
  labs(x = "Car Length", 
       y = "Car Height", 
       title = "Car Height vs Car Length")

m4 <- ggplot(data = car_data, aes(x = carwidth, y = curbweight, color = price)) + 
  geom_point() + 
  labs(x = "Car Width", 
       y = "Car Height", 
       title = "Car Height vs Car Width")

(m1+m2)/(m3+m4)
```

Due to the clear relationships between \textbf{citympg}/\textbf{highwaympg}, \textbf{carheight}/\textbf{carlength}, and \textbf{carheight}/\textbf{carwidth}, these interactions may be something to consider when creating the linear model. \textbf{Carwidth} and \textbf{carlength} seemed to have the weakest relationship but, should still be considered when making the model.

## Modeling Approach
The modeling approach we decided on was to select the final model covariates from the fourteen covariates that seemed to have a linear relationship with \textbf{price} in our bivariate analysis. A multiple linear regression model will be used because the outcome of car price is continuous and there are several covariates that have a linear relationship with \textbf{price}. We wanted to find the AIC and BIC for each combination of covariates to determine which selection of covariates would be best to use in our linear model. This helps us to prevent our model from overfitting. We wanted to search all possible models so we used the method dredge() from the MuMIn package to be able to create all the possible models from our covariates and order them by AIC and BIC values.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  lines <- options$output.lines
  if (is.null(lines)) {
    return(hook_output(x, options))  # pass to default hook
  }
  x <- unlist(strsplit(x, "\n"))
  more <- "..."
  if (length(lines)==1) {        # first n lines
    if (length(x) > lines) {
      # truncate the output, but add ....
      x <- c(head(x, lines), more)
    }
  } else {
    x <- c(more, x[lines], more)
  }
  # paste these lines together
  x <- paste(c(x, ""), collapse = "\n")
  hook_output(x, options)
})
```

### AIC
We want to choose the covariates for our model based on the lowest AIC value. In the block of code below, a model with the fourteen covariates is made. Then the model is tested with every possible combination of covariates and are ordered by AIC in ascending order. We selected the top 5 best models and recorded the covariates associated with them.
```{r best model AIC, echo=FALSE, message=FALSE, warning=FALSE, output.lines=1:12}

full.model <- lm(price ~ wheelbase+symboling+drivewheel+aspiration+cylindernumber+curbweight*carlength*carwidth+enginesize+horsepower+boreratio+fuelsystem+citympg*highwaympg, car_data, na.action = "na.fail")
dredge(full.model, rank = "AICc")

# AIC
# 1 carlength, curbweight, citympg, cylindernumber, drivewheel, enginesize, highwaympg, horsepower, carlength:curbweight
# 2 carlength, curbweight, citympg, cylindernumber, drivewheel, enginesize, highwaympg, horsepower, wheelbase, carlength:curbweight
# 3 carlength, curbweight, citympg, cylindernumber, drivewheel, enginesize, fuelsystem, highwaympg, horsepower, carlength:curbweight, citympg:highwaympg
# 4 carlength, curbweight, citympg, cylindernumber, drivewheel, enginesize, fuelsystem, highwaympg, horsepower, wheelbase, carlength:curbweight
# 5 carlength, curbweight, cylindernumber, drivewheel, enginesize, highwaympg, horsepower, wheelbase, carlength:curbweight
```

### BIC
As we mentioned above, we also wanted to evaluate based on BIC as a indicator of a good model. We repeated the same process by using the same model with all the covariates and doing a grid search using BIC which was ordered in ascending order. Similar to the AIC model, we took the 5 top models for BIC and recorded the variables associated with each model.

```{r best model BIC, echo=FALSE, message=FALSE, warning=FALSE, output.lines=1:12}

dredge(full.model, rank = "BIC")
# BIC
# 1 carlength, curbweight, drivewheel, enginesize, horsepower, carlength:curbweight
# 2 carlength, curbweight, drivewheel, enginesize, horsepower, wheelbase, carlength:curbweight
# 3 carlength, curbweight, drivewheel, enginesize, horsepower, symboling, carlength:curbweight
# 4 boreratio, carlength, curbweight, drivewheel, enginesize, horsepower, carlength:curbweight
# 5 carlength, curbweight, citympg, drivewheel, enginesize, highwaympg, horsepower, carlength:curbweight
```

After observing the top 5 multivariate linear models given by AIC and BIC, we looked to see the overlaps between the top models for each to determine the best model that has both a low AIC and BIC. The AIC top 5 models included much more features than the BIC models which is why we decided to select the BIC model that most closely resembled the AIC models. That model was number 5 on the BIC model which contained variables \textbf{carlength}, \textbf{curbweight}, \textbf{citympg}, \textbf{drivewheel}, \textbf{enginesize}, \textbf{highwaympg}, \textbf{horsepower}
\textbf{citympg}, \textbf{drivewheel}, \textbf{enginesize}, and \textbf{horsepower}. The model also includes the interaction between \textbf{carlength} and \textbf{curbweight} which was present in every AIC and BIC model.

### VIF

Next we ran VIF on the model to check for multicollinearity. \textbf{Carlength} had a VIF of 28.32, \textbf{curbweight} had a VIF of 253.92, and the \textbf{carlength}:\textbf{curbweight} interaction term had a VIF of 396.32. These are all greater than 10 so we removed \textbf{curbweight} from the model because it had a much larger VIF than \textbf{carlength}. \textbf{Citympg} and \textbf{highwaympg} also had a VIF greater than 10 which makes sense since these appear to be highly correlated features. Thus we decided to remove \textbf{citympg} from the model because it had a larger VIF than \textbf{highwaympg}. We then ran VIF again with the new selection of covariates and all of the VIF scores were below 10. See the second VIF table below to see the updated list of covariates that will be used for the final model.

```{r VIF, echo=FALSE, message=FALSE, warning=FALSE}
final.model <- lm(price ~ carlength*curbweight+citympg+drivewheel+enginesize+highwaympg+horsepower, car_data)

kable(vif(final.model), col.names = c('VIF'))
```


```{r final model after VIF, echo=FALSE, message=FALSE, warning=FALSE}
final.model <- lm(price ~ highwaympg+carlength+drivewheel+enginesize+horsepower, car_data)

kable(vif(final.model), col.names = c('VIF'))
```

## Output of Final Model
We created the final model Using the covariates we selected after evaluating AIC and BIC values of the model. The table below displays the coefficients for the final model. 

```{r anova table and model summary, echo=FALSE, message=FALSE, warning=FALSE}
final.model <- lm(price ~ highwaympg+carlength+drivewheel+enginesize+horsepower, car_data)
tidy(final.model, conf.int = TRUE) %>% 
  kable(format = "markdown", digits = 3)

```

## Assumptions
There are some assumptions that should be checked when using a multivariable linear model. These following assumptions should be checked:

* Linearity: Response variable has a linear relationship with predictor variables. There should be no pattern in the plots unless in the case for interaction terms.
  * Residuals vs Predicted Values
  * Residuals vs Every Predictor Variables

* Constant Variance: The regression is the same for all predictor variables. The height cloud of points should be constant across the x-axis or across all predictor variable values.
  * Residuals vs Predicted Values
  
* Normality: Response variable follows a Normal distribution around its mean for every predictor variable. The histogram should be approximately unimodal and symmetric and the points on the QQ Plot should follow on the diagonal line.
  * Histogram of Residuals
  * Normal QQ-Plot of Residuals
  
* Independence: All observations are independent. There should not be pattern in residuals across the order of observations.
  * Residuals vs Observation Number

### Linearity

```{r linear assumption, echo=FALSE, message=FALSE, warning=FALSE}
car_aug <- augment(final.model)
l1 = ggplot(data = car_aug, aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "red") +
  labs(x = "Predicted", y = "Residuals", title = "Residuals vs. Predicted")

l2 = ggplot(data = car_aug, aes(x = carlength, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "red") +
  labs(x = "Car Length", y = "Residuals", title = "Residuals vs. Car Length")

l3 = ggplot(data = car_aug, aes(x = drivewheel, y = .resid)) +
  geom_boxplot() +
  geom_hline(yintercept = 0, color = "red") +
  labs(x = "Drive Wheel", y = "Residuals", title = "Residuals vs. Drive Wheel")

l4 = ggplot(data = car_aug, aes(x = enginesize, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "red") +
  labs(x = "Engine Size", y = "Residuals", title = "Residuals vs. Engine Size")

l5 = ggplot(data = car_aug, aes(x = horsepower, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "red") +
  labs(x = "Horsepower", y = "Residuals", title = "Residuals vs. Horsepower")

l6 = ggplot(data = car_aug, aes(x = highwaympg, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "red") +
  labs(x = "Highway MPG", y = "Residuals", title = "Residuals vs. Highway MPG")

(l1)
(l2+l3)/(l4+l5+l6)
```

Based on the plots for checking the linearity assumption, it seems that the model does not fulfill the linearity assumption since there is a fan pattern in almost every predictor variable. Residuals tend to either increase or decrease as a predictor variable increases so it would seem the linearity assumption is not fulfilled. This also goes for the residuals versus predicted plots where there is also a fan pattern.

### Constant Variance

```{r constant variance, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = car_aug, aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "red") +
  labs(x = "Predicted", y = "Residuals", title = "Residuals vs. Predicted")

```
The model does not meet the constant variance assumption since the graph does not follow a constant variance across all predicted variables. The variance of the residuals tend to increase as the predicted variables increase so it has a fanning pattern.

### Normal Condition
```{r normal condition, echo=FALSE, message=FALSE, warning=FALSE}
n1 = ggplot(data = car_aug, aes(x = .resid)) +
  geom_histogram() +
  labs(x = "Residuals", title = "Distribution of Residuals")

n2 = ggplot(data = car_aug, aes(sample = .resid)) +
  stat_qq() +
  stat_qq_line() +
  labs(title = "Normal QQ Plot of Residuals")

n1+n2
```
The normal condition is not met since the QQ Plot is not following a completely diagonal line. The tails of the QQ plot are not on the diagonal line. Since the histogram of the residual is not normal and the QQ Plot is not following the diagonal on the tails, therefore the normal condition is not met for the model.

### Independence

```{r independence condition, echo=FALSE, message=FALSE, warning=FALSE}
car_aug <- car_aug %>% 
  mutate(obs_num = 1:nrow(car_aug))
ggplot(data = car_aug, aes(x = obs_num, y = .resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, color = "red") +
  labs(x = "Observation Number",
       y = "Residuals",
       title = "Residuals vs. Observation Number")
```

The independence condition is met in our case since across the order of observations, there is constant variance. This means that the observations are most likely independent from one another.

## Interpretations of Model Coefficients

The next part in our analysis is going to refer back to the coefficients in our model. Here is the table of coefficients.

```{r model coefficients, echo=FALSE, message=FALSE, warning=FALSE}
tidy(final.model, conf.int = TRUE) %>% 
  kable(format = "markdown", digits = 3)
```

$y = \beta_{0} + \beta_{1}X_{1} + \beta_{2}X_{2} + \beta_{3}X_{3} + \beta_{4}X_{4} + \beta_{5}X_{5} + \beta_{6}X_{6} + \varepsilon$

$y = -20177.318 + 35.703X_{1} + 84.491X_{2} - 1262.343X_{3} + 1258.834X_{4} + 98.617X_{5} + 51.937X_{6} + \varepsilon$

Based on the table of the linear model above, the estimate intercept is telling us the price of a car with a \textbf{carlength} of 0, \textbf{enginesize} of 0, \textbf{highwaympg} of 0, \textbf{horsepower} of 0, and \textbf{4wd} which is not realistic at all. The intercept estimate, -20177.318 does not tell us anything meaningful relative towards the data model. For the coefficients, if a car's \textbf{drivewheel} is \textbf{fwd} then the price prediction does down \$1262.34 and if a its \textbf{drivewheel} is \textbf{rwd} then the price prediction does up \$1262.34. The coefficient estimate 98.617 for engine size means that the for one unit increase in the \textbf{enginesize} there is a general increase of \$98.62 in car price. The coefficient estimate 35.703 for \textbf{highwaympg} means that for every one unit increase \textbf{highwaympg}, the car price will increase by about \$35.70. The coefficient estimate for \textbf{horsepower} is 51.937 which means that for every one unit increase in \textbf{horsepower}, there is an increase of about \$51.94 in car price. The coefficient estimate 84.491 for \textbf{carlength} means that for one unit increase in \textbf{carlength}, there is a general increase of \$84.49 in car price.

## Limitations
There are a few limitations of the model that should be acknowledged when trying to predict car price. To begin with, the model will not be able to accurately predict the price of a car that has covariate values outside the range of values that the model was trained on. For example, the final model was trained on the variable \textbf{carlength} which ranged from 140 to 200. Thus it would not be wise to predict the price of car with a \textbf{carlength} outside the range [140,200]. In other words, the model can interpolate but not extrapolate. Another limitation is that this model can only fit data linearly. Even though this dataset fits a linear model well, there might be non linear models that can predict \textbf{price} at a much higher accuracy. 

## Additional Work

Univariate and bivariate plots for \textbf{carname}.

```{r add work, echo=FALSE, message=FALSE, warning=FALSE}
p7/b7
```


